---
title: "Welcome"
---

Unlock the power of handwriting analysis with handwriter. This tool is designed to assist forensic examiners by analyzing handwritten documents. Whether you are a forensic document examiner, legal professional, academic, or simply curious about how statistics are applied to handwriting, handwriter provides an automated way to evaluate handwriting samples.

# Quick Start

## Installation

Handwriter requires R, RStudio IDE, and JAGS.

-   Install R and RStudio from [POSIT](https://posit.co/download/rstudio-desktop/)
-   Install JAGS from [SourceForge](https://sourceforge.net/projects/mcmc-jags/files/)

Install the handwriterApp R package. Open RStudio and navigate to the console window and type

```{r, eval=FALSE}
options(timeout = 100000)
install.packages("devtools")
install.packages("CSAFE-ISU/handwriterApp")
devtools::install_github("CSAFE-ISU/handwriterRF")
```

## Launch the App

Open RStudio, navigate to the console window, and type:

```{r, eval = FALSE}
library(handwriterApp)
library(handwriterRF)
handwriterApp()
```

In the pop-up window, click **Open in Browser**. If you use the app in the pop-up window instead of in a browser, some links will not work.

## Choose a Scenario

Handwriter addresses two scenarios. Choose the option that best describes your handwriting:

```{=html}
<div class="twocards">

<div class="card">
  <div class="container">
    <h3>SCENARIO 1</h3>
    <p>
    <i>Compare a questioned document to another handwritten document.</i>
    </p>
    
    <hr>
    
    <p>
    <b>Requirements</b>
      <ul>
        <li>
        <b>Questioned Document:</b> from an unknown writer.
        </li>
        <li>
        <b>Comparison Document:</b> from a known or unknown writer.
        </li>
      </ul>
    </p>
    
    <p>
    <b>Result:</b> A score-based likelihood ratio that expresses the support of the evidence in favor of the samples having been written by the same writer or different writers.
    </p>
  </div>
</div>

<div class="card">
  <div class="container">
    <h3>SCENARIO 2</h3>
    
    <p>
    <i>Compare a questioned document to a group of known handwriting samples.</i>
    </p>
    
    <hr>
    
    <p>
    <b>Requirements</b>
      <ul>
        <li>
        <b>Questioned Document:</b> from an unknown writer.
        </li>
        <li>
        <b>Additional Documents:</b> Three known writing samples from each writer in a group of potential writers. The questioned document MUST have been written by someone in this group.
        </li>
      </ul>
    </p>
    
    <p>
    <b>Result:</b> The posterior probability that each potential writer wrote the questioned document.
    </p>
  </div>
</div>

</div>
```
