---
title: "Welcome"
---

Unlock the power of handwriting analysis with handwriter. This tool is designed to assist forensic examiners by analyzing handwritten documents. Whether you are a forensic document examiner, legal professional, academic, or simply curious about how statistics are applied to handwriting, handwriter provides an automated way to evaluate handwriting samples.

# Quick Start

## Installation

Handwriter requires R, RStudio IDE, and JAGS.

-   Install R and RStudio from [POSIT](https://posit.co/download/rstudio-desktop/)
-   Install JAGS from [SourceForge](https://sourceforge.net/projects/mcmc-jags/files/)

Install the handwriterApp R package. Open RStudio and navigate to the console window and type

```{r, eval=FALSE}
options(timeout = 100000)
install.packages("devtools")
install.packages("CSAFE-ISU/handwriterApp")
devtools::install_github("CSAFE-ISU/handwriterRF")
```

## Launch the App

Open RStudio, navigate to the console window, and type:

```{r, eval = FALSE}
library(handwriterApp)
library(handwriterRF)
handwriterApp()
```

In the pop-up window, click **Open in Browser**. If you use the app in the pop-up window instead of in a browser, some links will not work.

## Choose a Scenario

Handwriter addresses two scenarios. Choose the option that best describes your handwriting:
